Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex
Fixing mean issue
minor fixes for clg stuff

\begin{table}[hbtp]
\centering
{\footnotesize % feels bad man but it's definitely easier than most other alternatives
\caption{Regex vs. Comby for Python.   LOC describes the project files considered. Muts. is total number of mutants generated for those files. \clg{FIXME: what's an invalid mutant for python?}  We can use TCE to check for redundant Python mutants, shown under ``Red.''}
\label{tab:table_python1}
\begin{tabularx}{\columnwidth}{l|r|rcr|rcr}
\toprule\toprule
                 &                 & \multicolumn{3}{c|}{\textbf{Regex}}             &\multicolumn{3}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC}    & \textbf{Muts.} & \textbf{Red.}  & \textbf{\% Valid} & \textbf{Muts.} & \textbf{Red.}   &  \textbf{\% Valid} \\\midrule
keract           & 402             & 3984  & 729   & 41.53\%           & 3067  & 533    & 47.96\% \\
dtw              & 118             & 2106  & 567   & 46.20\%           & 1835  & 639    & 47.19\% \\
notion-          & \mr{2}{189}     & \mr{2}{1038}  & \mr{2}{82}    & \mr{2}{18.89\%}           & \mr{2}{1019}  & \mr{2}{122}    & \mr{2}{19.23\%} \\
sdk-py           & & & & & & \\[0.5ex]
atlassian-       & \mr{2}{236}      & \mr{2}{1511}  & \mr{2}{207}   & \mr{2}{19.99\%}           & 1319  & \mr{2}{351}    & \mr{2}{25.25\%} \\
python-api       & & & & & & \\[0.5ex]
ESD              & 698             & 6268  & 1642  & 29.46\%           & 3874  & 614    & 44.18\% \\
fiber            & 358             & 1565  & 163   & 31.08\%           & 1466  & 241    & 31.24\% \\\bottomrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrrrrr}
                  && &  \textbf{Red.}     & \textbf{Valid}  & \textbf{Invalid}  & \textbf{\% Valid} \\\midrule
\multirow{4}{*}{\textbf{Overall}} & \multirow{2}{*}{Regex} & Mean &  565.00 & 913.00 & 1267.33 & 31.19\%  & \\
    &   &  Std.Dev. & 584.79  & 708.93 & 813.35 & 11.06\%  \\
 & \multirow{2}{*}{Comby} & Mean & 839.33 & 840.67 & 416.67 & 35.84\% \\
  &   &  Std.Dev. &  211.62 & 628.79 & 418.99 & 12.28\%   \\\bottomrule
\end{tabularx}}
\end{table}

@@

\begin{table}[htbp]
\centering
\caption{Java (Our Implementation vs. PIT vs. LittleDarwin). \clg{FIXME: explain why no eqv for PIT.} LittleDarwin produces no equivalent mutants.\clg{right?}}
\label{tab:table_java2}
\resizebox{\columnwidth}{!}{% again don't love it, but footnotesize is actually smaller than necessary
\begin{tabular}{l|rrr|rr|rr}
\toprule
                 & \mc{3}{c|}{\textbf{Comby}}   & \mc{2}{c|}{\textbf{PIT}} & \mc{2}{c}{\textbf{LittleDarwin}} \\
\textbf{Project} & \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} \\ \midrule

@@

\begin{table}[htbp]
\centering
{\small
\caption{Rust (Our Implementation vs. Cargo-Mutants)}
\label{tab:table_rust2}
\begin{tabularx}{\columnwidth}{X|rrr|rrr}
\toprule
        & \multicolumn{3}{c|}{\textbf{Comby}}  & \multicolumn{3}{c}{\textbf{Cargo-Mutants}} \\ 
\textbf{Project} & \textbf{Muts.} & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} & \textbf{Muts.} & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} \\\midrule
cargo release & 1690 & 0.80 & 0\% & 5 & 0.40 & 0\%   \\
passarine & 173 & 0.52 & 50\% & 0 & 0.00 & 0\%   \\
typos & 366 & 0.77 & 20\% & 6 & 0.83 & 0\%   \\
ord & 643 & 0.83 & 20\% & 6 & 1.00 & 0\%   \\
bazuka & 402 & 0.73 & 0\% & 0 & 0.00 & 0\%   \\
strum & 50 & 0.22 & 40\% & 2 & 1.00 & 0\%   \\\midrule
\textbf{Mean}   & 554.00 & 0.64 & 22.00\% & 3.17 & 0.54 & 0.00\%\\
\textbf{Std. Dev} & 592.63 & 0.25 & 20.41\%   & 2.86 & 0.47 & 0.00\% \\\bottomrule
\end{tabularx}
}
\end{table}

>>>>

\begin{table}[hbtp]
\centering
{\footnotesize % feels bad man but it's definitely easier than most other alternatives
\caption{Regex vs. Comby for Python.   LOC describes the project files
  considered. Muts. is total number of mutants generated for those
  files.  Invalid mutants are ones that fail module load (e.g., due
  to imbalanced parenthesis, bad indentation, or similar problems).  We can use TCE to check for redundant Python mutants, shown under ``Red.''}
\label{tab:table_python1}
\begin{tabularx}{\columnwidth}{l|r|rcr|rcr}
\toprule\toprule
                 &                 & \multicolumn{3}{c|}{\textbf{Regex}}             &\multicolumn{3}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC}    & \textbf{Muts.} & \textbf{Red.}  & \textbf{\% Valid} & \textbf{Muts.} & \textbf{Red.}   &  \textbf{\% Valid} \\\midrule
keract           & 402             & 3984  & 729   & 41.53\%           & 3067  & 533    & 47.96\% \\
dtw              & 118             & 2106  & 567   & 46.20\%           & 1835  & 639    & 47.19\% \\
notion-          & \mr{2}{189}     & \mr{2}{1038}  & \mr{2}{82}    & \mr{2}{18.89\%}           & \mr{2}{1019}  & \mr{2}{122}    & \mr{2}{19.23\%} \\
sdk-py           & & & & & & \\[0.5ex]
atlassian-       & \mr{2}{236}      & \mr{2}{1511}  & \mr{2}{207}   & \mr{2}{19.99\%}           & 1319  & \mr{2}{351}    & \mr{2}{25.25\%} \\
python-api       & & & & & & \\[0.5ex]
ESD              & 698             & 6268  & 1642  & 29.46\%           & 3874  & 614    & 44.18\% \\
fiber            & 358             & 1565  & 163   & 31.08\%           & 1466  & 241    & 31.24\% \\\bottomrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrrrrr}
                  && &  \textbf{Red.}     & \textbf{Valid}  & \textbf{Invalid}  & \textbf{\% Valid} \\\midrule
\multirow{4}{*}{\textbf{Overall}} & \multirow{2}{*}{Regex} & Mean &  565.00 & 913.00 & 1267.33 & 31.19\%  & \\
    &   &  Std.Dev. & 584.79  & 708.93 & 813.35 & 11.06\%  \\
 & \multirow{2}{*}{Comby} & Mean & 839.33 & 840.67 & 416.67 & 35.84\% \\
  &   &  Std.Dev. &  211.62 & 628.79 & 418.99 & 12.28\%   \\\bottomrule
\end{tabularx}}
\end{table}

@@

\begin{table}[htbp]
\centering
\caption{Java (Our Implementation vs. PIT vs. LittleDarwin).
  Determining it PIT bytecode mutants are equivalent is extremely
  difficult to do with reasonable accuracy, so we did not attempt it.  LittleDarwin produces no equivalent mutants.}
\label{tab:table_java2}
\resizebox{\columnwidth}{!}{% again don't love it, but footnotesize is actually smaller than necessary
\begin{tabular}{l|rrr|rr|rr}
\toprule
                 & \mc{3}{c|}{\textbf{Comby}}   & \mc{2}{c|}{\textbf{PIT}} & \mc{2}{c}{\textbf{LittleDarwin}} \\
\textbf{Project} & \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} \\ \midrule

@@

\begin{table}[htbp]
\centering
{\small
\caption{Rust (Our Implementation vs. Cargo-Mutants)}
\label{tab:table_rust2}
\begin{tabularx}{\columnwidth}{X|rrr|rrr}
\toprule
        & \multicolumn{3}{c|}{\textbf{Comby}}  & \multicolumn{3}{c}{\textbf{Cargo-Mutants}} \\ 
\textbf{Project} & \textbf{Muts.} & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} & \textbf{Muts.} & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} \\\midrule
cargo release & 1690 & 0.80 & 0\% & 5 & 0.40 & 0\%   \\
passarine & 173 & 0.52 & 50\% & 0 & 0.00 & 0\%   \\
typos & 366 & 0.77 & 20\% & 6 & 0.83 & 0\%   \\
ord & 643 & 0.83 & 20\% & 6 & 1.00 & 0\%   \\
bazuka & 402 & 0.73 & 0\% & 0 & 0.00 & 0\%   \\
strum & 50 & 0.22 & 40\% & 2 & 1.00 & 0\%   \\\midrule
\textbf{Mean}   & 554.00 & 0.64 & 21.67\% & 3.17 & 0.54 & 0.00\%\\
\textbf{Std. Dev} & 592.63 & 0.25 & 20.41\%   & 2.86 & 0.47 & 0.00\% \\\bottomrule
\end{tabularx}
}
\end{table}
